Survival Compass: Statistical Insights into Lung Cancer Patients' Journey Post-Diagnosis

### 2024-04-04 paper/paper.qmd
woking on data section - tyring to fix pathogenic stage bar chart

# 1. Add the desired font (e.g., Patrick Hand)
font_add_google("Patrick Hand", "patrick")

# 2. Set the font for ggplot
showtext_auto()

@@

@@

###########################

# Define color palette for different stages
stage_colors <- c("Early" = "#FFB6C1", "Intermediate" = "#FF69B4", "Advanced" = "#FF1493")

# Modify data to ensure correct ordering of stages
analysis_data$pathogenic_stage <- factor(analysis_data$pathogenic_stage, levels = c("Early", "Intermediate", "Advanced"))

# Create bar chart for pathogenic_stage
pathogenic_stage_counts <- analysis_data %>%
  group_by(pathogenic_stage) %>%
  summarise(count = n ()) %>%
  mutate(percentage = count / sum(count) * 100) %>%
  arrange(desc(pathogenic_stage))

# Plot the data
ggplot(pathogenic_stage_counts, aes(x = pathogenic_stage, y = percentage, fill = pathogenic_stage)) +
  geom_bar(stat = "identity") +
  labs(title = "Percentage of Patients by Pathogenic Stage",
       x = "Pathogenic Stage",
       y = "Percentage") +
  scale_fill_manual(values = stage_colors) +  # Apply color palette
  theme_minimal() +
  theme(
    text = element_text(family = "patrick")  # Set font to Patrick Hand
  )

>>>>

# Add the desired font (e.g., Patrick Hand)
font_add_google("Patrick Hand", "patrick")

# Set the font for ggplot
showtext_auto()

@@

# Replace NA values with your desired stages
analysis_data <- analysis_data %>%
  mutate(pathogenic_stage = ifelse(is.na(pathogenic_stage), 
                                   c('Stage I', 'Stage IA', 'Stage IB', 
                                     'Stage II', 'Stage IIA', 'Stage IIB', 
                                     'Stage III', 'Stage IIIA', 'Stage IIIB', 
                                     'Stage IV'), 
                                   pathogenic_stage))

@@
